simulation & inference of transients

### 2019-07-12 notebook/ghost-sims.Rmd
add may outbreak model

```{r message = FALSE}
library(tidyverse)
library(furrr)
library(nimble)
```

```{r}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 4e3, x0 = 0.2)
growth <- function(x, p) x * p$r * (1 - x / p$K)
consumption <- function(x, p) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
```

```{r}
theory <- 
  tibble(x= seq(0,2, length.out = 100)) %>%
  mutate(g = growth(x,p), 
         c = consumption(x,p)) %>%
  mutate(potential = - cumsum(g - c)) %>%
  gather(curve, y, -x, -potential) 
```

```{r noisy_switch}
theory %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd=1)
```

```{r}
theory %>%
  ggplot(aes(x, potential)) + 
  geom_line(lwd=1)
```

@@

stochastic_sim <- function(f, p){
  x <- numeric(p$N)
  x[1] <- p$x0
  dBt <- rnorm(p$N, 0, p$sigma)
  for(t in 1:(p$N-1)){
    x[t+1] <- max( 
                  f(x[t], p) + dBt[t],
                  0)
  }
  data.frame(t = 1:p$N, x)
}

@@

>>>>

```{r message = FALSE}
library(tidyverse)
library(furrr)
```

```{r}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 4e3, x0 = 0.2, N = 1e4)
growth <- function(x, p) x * p$r * (1 - x / p$K)
consumption <- function(x, p) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
```

```{r}
theory <- 
  function(p){
    tibble(x= seq(0,2, length.out = 100)) %>%
    mutate(g = growth(x,p), 
           c = consumption(x,p)) %>%
    mutate(potential = - cumsum(g - c)) %>%
    gather(curve, y, -x, -potential) 
}
```

```{r noisy_switch}
theory(p) %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd=1)
```

```{r}
theory(p) %>%
  ggplot(aes(x, potential)) + 
  geom_line(lwd=1)
```

@@

stochastic_sim <- function(f, p){
  x <- numeric(p$N)
  x[1] <- p$x0
  dBt <- rnorm(p$N, 0, p$sigma)
  for(t in 1:(p$N-1)){
    x[t+1] <- max( 
                  f(x[t], p) + x[t] * dBt[t],  # arguably x[t] * dB[t] would be a better model!
                  0)
  }
  data.frame(t = 1:p$N, x)
}

@@

```{r}
a <- c(0.0225, 0.0230, 0.02305, 0.0231)
names(a) <- a

df <- map_dfr(a, function(a){
  p$a <- a
  p$N <- 1e4
  det_sim(may, p)
},
.id = "a")

df %>% ggplot(aes(t,x, col = a)) + geom_line() + coord_cartesian(xlim=c(0,1000))

theory(p) %>% ggplot(aes(x, y, col=curve)) + geom_line(lwd=1)
